Blum axioms and nondeterministic computation of functions

### 2016-04-19 paper.tex
paper.tex: Add concluding remarks.

>>>>

Krentel note that both his and Valiant's definition
arise from applying an associative operator
to all values returned in the branches of computation
--- maximum/minimum in Krentel's case,
and cardinality (counting) in Valiant's case.
Therefore, using other associative operations yield alternative definitions
of nondeterministic function computation \cite[p.~493]{Krentel1988}.

\section{Concluding Remarks}

As we have seen,
it is possible to associate nondeterministic Turing machines
with function computation,
although the association is not so straightforward as with deterministic machines.

Through the use of the notions of acceptable Gödel numberings
and Blum axioms,
we formalized the notion of ``reasonable'' definition
for nondeterministic function computation,
and by consequence we formalized what is a ``generalization of $\NP$ to functions''.
Krentel's and Valiant's definitions,
besides generalizing $\NP$, in particular,
also allow for a flexible generalization of $\NP$-completeness
--- that is, they allow for interesting problems to be ``functionally $\NP$-complete'',
under each definition.
